International Relations are a Social Network:\\ A Latent Network Approach for Global Politics

### 2017-10-19 paper/4_app.tex
checking compliation
noch mal ins feur.

\begin{table}
\caption{Features of the Studies Re-estimated. }
	\begin{tabular}{lcccccc}
& Model &  N. Actors  & N. Dyads & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
Reiter \& Stam (2003) & Logit & 193 & $753,456$ & Directed & Robust \\	
McDonald (2004) & Logit & 198 & $92,354$ & Undirected & Robust\\
Rose (2004) & OLS & 177 & $234,597$ & Directed & Robust \\	 
Weeks (2012) & Logit & 197 &  $901,540$ & Directed & Robust \\
Gibler (2017) & Logit & 193 &    & $650,557$ & UnDirected & none \\ \bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Here we provide a brief summary of the key variable in each of the five replications and a note about whether or not the finding is replicated when using our network based approach. Cases in which the substantive finding is not replicated are highlighted in bold.}
\begin{tabular}{l p{7cm} l} \toprule
\multirow{2}{*}{Study} & \multirow{2}{*}{Central Finding} & Does it Replicate \\ 
	& &  in a Network Model? \\ \toprule
Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & Replicates \\ \midrule
McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & \textbf{Fails to Replicate} \\ \midrule
Rose (2004) & WTO Membership Does not Effect Trade & Replicates \\ \midrule
Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & \textbf{Fails to Replicate} \\\midrule
Gibler (2017) & Power Parity at Time of Entry to International System Inceases Conflict & \textbf{Fails to Replicate} \\ \bottomrule
	\end{tabular}
			\label{tab:modelFindingSumm}
\end{table}

@@

In the original model, the variable ``Pers/Democ Directed Dyad" (which represents a Personalist $\rightarrow$ Democractic directed dyad) is clearly positive while the variable ``Democ/Personalist Directed Dyad'' is zero and the difference between the two coefficients is clearly distinct from zero. In our re-estimation using the AME framework, we also find that Pers-Democ directed dyad has a positive effect with zero excluded from the 95\% confidence interval while Democ-Pers directed dyad is indistinguishable from zero. Using this model, however, we can no longer conclusively say that the Pers/Democratic coefficient is larger than the Democ/Personalist one.
Our re-extimation using the AME approach therefore cast some doubt on Reiter \& Stam's key claim that MIDs initiated by personalist dictatorships against democracies are more likely than MIDS initiated by democracies. Further, the effect of most of the covariates in the literature thought to predict interstate MIDs are much closer to zero when using the AME framework. Finally, our modeling approach outperforms the original model by better, and more accurately, predicting MIDs out-of-sample (Figure~\ref{fig:reitaucpr} and Figure ~\ref{fig:reitpr}).

\begin{figure}
\includegraphics[width=\textwidth]{reiter_coefs_all.pdf}
\caption{\label{fig:reitCoef} Coefficient plot of Reiter \& Stam (2003)'s original model (blue) compared to AME model (red). }
\end{figure}

\begin{figure}
\centering   
\subfigure[AUC]{\label{fig:reitauc}\includegraphics[width=65mm]{reiter_auc_outsamp.pdf}}
\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{reiter_pr_outsamp.pdf}}
\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}

\floatbarrier
\subsection{Replication of McDonald (2004)}

@@

% sd.rowmean sd.colmean   dyad.dep  triad.dep 
% 0.03210221 0.03210221 0.99362646 0.00130249 
\begin{figure}
\caption{\label{fig:gibler:dyadtriad} The left panel is  a plot of the dyadic dependencies in the Gibler model 6; the right panel shows the triad dependencies.  Note that the red line represents the null hypothesis of no dependencies, indicating that the standard logistic approach is far from what is uncovered with this analysis. }
\includegraphics[width=\textwidth]{netplots}
\end{figure}
\FloatBarrier

>>>>

\begin{table}
\caption{Features of the Studies Re-estimated. }
	\begin{tabular}{lcccccc}
& Model &  Date Range & N. Actors  & N. Dyads & Dyads Type & Clustering $\sigma_{\hat{\beta}}$ \\ \toprule
Reiter \& Stam (2003) &Logit &1945--1995 &  193 & $753,456$ & Directed & Robust \\	
McDonald (2004) & Logit &1959--2002 & 198 & $92,354$ & Undirected & Robust\\
Rose (2004) & OLS & 1948--1999 & 177 & $234,597$ & Directed & Robust \\	 
Weeks (2012) & Logit & 1946--1999 &197 &  $901,540$ & Directed & Robust \\
Gibler (2017) & Logit & 1816--2008 &193 &   $650,557$ & UnDirected & none \\ \bottomrule
	\end{tabular}
\end{table}

@@

\begin{table}[ht]
\centering
\caption{Here we provide a brief summary of the key variable in each of the five replications and a note about whether or not the finding is replicated when using our network based approach. Cases in which the substantive finding is not replicated are highlighted in bold.}
\begin{tabular}{l p{7cm} l} \toprule
\multirow{2}{*}{Study} & \multirow{2}{*}{Central Finding} &  Replicates \\ 
	& &  in a Network Model? \\ \toprule
Reiter \& Stam (2003) & Personalist Regimes Attack Democracies, Not Vice Versa & {Replicates} \\ \midrule
McDonald (2004) & Lower Trade Barriers and Higher Trade Lead to Peace & {Does Not Replicate}\\ \midrule
Rose (2004) & WTO Membership Does not Effect Trade & {Replicates}\\ \midrule
Weeks (2012) & Bosses, Juntas and Strongmen are more Aggressive, Machines are Not & {Does Not Replicate} \\\midrule
Gibler (2017) & Power Parity at Time of Entry to International System Inceases Conflict & {Does Not Replicate} \\ \bottomrule
	\end{tabular}
			\label{tab:modelFindingSumm}
\end{table}

@@

In the original model, the variable ``Pers/Democ Directed Dyad" (which represents a Personalist $\rightarrow$ Democractic directed dyad) is clearly positive while the variable ``Democ/Personalist Directed Dyad'' is zero and the difference between the two coefficients is clearly distinct from zero. In our re-estimation using the AME framework, we also find that Pers-Democ directed dyad has a positive effect with zero excluded from the 95\% confidence interval while Democ-Pers directed dyad is indistinguishable from zero. Using this model, however, we can no longer conclusively say that the Pers/Democratic coefficient is larger than the Democ/Personalist one.
Our re-estimation using the AME approach therefore cast some doubt on Reiter \& Stam's key claim that MIDs initiated by personalist dictatorships against democracies are more likely than MIDS initiated by democracies. Further, the effect of most of the covariates in the literature thought to predict interstate MIDs are much closer to zero when using the AME framework. Finally, our modeling approach outperforms the original model by better, and more accurately, predicting MIDs out-of-sample (Figure~\ref{fig:reitaucpr}).

%\begin{figure}
%%\includegraphics[width=\textwidth]{reiter_coefs_all.pdf}
%\caption{\label{fig:reitCoef} Coefficient plot of Reiter \& Stam (2003)'s original model (blue) compared to AME model (red). }
%\end{figure}

\begin{figure}
\centering   
\subfigure[AUC]{\label{fig:reitaucpr}\includegraphics[width=65mm]{reiter_auc_outsamp.pdf}}
\subfigure[Precision and Recall]{\label{fig:reitpr}\includegraphics[width=65mm]{reiter_pr_outsamp.pdf}}
\caption{Assessments of out-of-sample predictive performance for Reiter \& Stam (2003) using ROC curves and PR curves.}
\end{figure}

\subsection{Replication of McDonald (2004)}

@@

% sd.rowmean sd.colmean   dyad.dep  triad.dep 
% 0.03210221 0.03210221 0.99362646 0.00130249

NEW GRAPHICS TO COME AND BE DESCRIBED.

\begin{figure}
\caption{\label{fig:gibler:dyadtriad} The left panel is  a plot of the dyadic dependencies in the Gibler model 6; the right panel shows the triad dependencies.  Note that the red line represents the null hypothesis of no dependencies, indicating that the standard logistic approach is far from what is uncovered with this analysis. }
\includegraphics[width=\textwidth]{netplots}
\end{figure}
\FloatBarrier
